TADCompare: an R package for differential analysis and characterization of Topologically Associated Domains

### 2019-11-05 manuscript/manuscript.Rmd
Spacing fix
Make formatting to conform BMC Bioinformatics

---
bibliography: [references/networks.bib,references/brain.bib,references/enrichment.bib,references/3D_refs.bib]
csl: styles.ref/genomebiology.csl
output:
  word_document:
    reference_docx: styles.doc/Arial_11_single_space_normal_margins.docx
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

@@

"Rheumatoid arthritis", "Systemic Lupus Erythematosus", and "Systemic sclerosis" were the most coherent in the "Autoimmune" category (0.86, 0.80, 0.79, respectively). On the other end of the coherence spectrum, "Allergic rinitis" and "Atopic dermatitis" were the least coherent (0.51, 0.60, respectively). The average coherence of autoimmune diseases was high, 0.70 (Table 1), with all autoimmune diseases, except "Allergic rinitis", having coherence estimates > 0.60 (Supplementary Table S3). Diseases in the "Neurologic" category were similarly highly coherent (average coherence 0.72). However, the average coherence of neurologic disorders using STRING database was 0.49, suggesting that, with larger number of networks being estimated the overall coherence of neurologic diseases is low. "Alzheimer's disease" and "Parkinson's disease" were the most coherent (0.88 and 0.84, respectively), while "Migraine" was the least coherent (0.54). Diseases in the "Eye disease" category were more heterogeneous, with coherence ranging from 0.35 for "Corneal astigmatism" to 1.01 for "Refractive error". The average coherence of diseases in the "Eye disease" category was relatively high (0.66). 
+-------+
| ![](Figures/Fig4_summary_diseases.png)      |
| **Figure 4. Coherence estimates of diseases.** Size of dots represents the level of normalized coherence (X-axis) for individual diseases (Y-axis).   |
+-------+

>>>>

---
bibliography: [references/networks.bib,references/brain.bib,references/enrichment.bib,references/3D_refs.bib]
csl: styles.ref/genomebiology.csl
output:
  word_document:
    reference_docx: styles.doc/BMC_Bioinformatics.docx
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---

@@

"Rheumatoid arthritis", "Systemic Lupus Erythematosus", and "Systemic sclerosis" were the most coherent in the "Autoimmune" category (0.86, 0.80, 0.79, respectively). On the other end of the coherence spectrum, "Allergic rinitis" and "Atopic dermatitis" were the least coherent (0.51, 0.60, respectively). The average coherence of autoimmune diseases was high, 0.70 (Table 1), with all autoimmune diseases, except "Allergic rinitis", having coherence estimates > 0.60 (Supplementary Table S3). Diseases in the "Neurologic" category were similarly highly coherent (average coherence 0.72). However, the average coherence of neurologic disorders using STRING database was 0.49, suggesting that, with larger number of networks being estimated the overall coherence of neurologic diseases is low. "Alzheimer's disease" and "Parkinson's disease" were the most coherent (0.88 and 0.84, respectively), while "Migraine" was the least coherent (0.54). Diseases in the "Eye disease" category were more heterogeneous, with coherence ranging from 0.35 for "Corneal astigmatism" to 1.01 for "Refractive error". The average coherence of diseases in the "Eye disease" category was relatively high (0.66).

+-------+
| ![](Figures/Fig4_summary_diseases.png)      |
| **Figure 4. Coherence estimates of diseases.** Size of dots represents the level of normalized coherence (X-axis) for individual diseases (Y-axis).   |
+-------+
